Behavior Driven Development in Haskell

### 2012-05-29 paper.tex
Remove a note
"Introduction"

\emph{IMPORTANT: sol: I have to release a new version of hspec, that
includes the Specs-to-Spec and hspecX-to-hspec changes.  Otherwise the
code in this paper will not work!}

@@

Haskell programmers, however, is apt to rely on the type system too
much and tend not to write test code.  For example, the Haskell
Platform 2011.4.0.0 contains 23 packages (not counting the 19 core
libraries that come with GHC), but only 8 of them a test suite (5
provide example code, 10 have no tests nor examples).  Lacking test
code also means that typical usage examples are not provided.

@@

In BDD, all behavior should be documented, together with some
\emph{evidence} for that behavior.  Most existing BDD tools use
\emph{code examples} as evidence for behavior.
Hspec, a BDD tool for Haskell inspired by RSpec~\cite{rspec}, supports
both code examples and \emph{properties} as evidence.
It can verify examples and tests properties, and it can create an
informal specification document from that.

@@

Both, Doctest and Hspec miss some features.  So we extend them as
needed.  Our contributions are:

@@

\item
    Introduce a set of combinators to set expectations about
    code examples for use with Hspec. (Section \ref{sec:code-doc} and Section \ref{sec:hspec-comb})

@@

\item
    Show best current practice of BDD in Haskell using Doctest and
    Hspec (Section \ref{ref:Best-current-practice})

@@

\item[developer]
    A programmer who develops a library.

@@

@@

\item[spec]
    TBD: BDD terminology for test suite.

>>>>

@@

Haskell programmers, however, is apt to rely on the type system too
much and tend not to write test code.  For example, the Haskell
Platform 2011.4.0.0 contains 23 packages (not counting the 19 core
libraries that come with GHC), but only 8 of them have a test suite (5
provide example code, 10 have no tests nor examples).  Lacking test
code also means that typical usage examples are not provided.

@@

In BDD, all behavior should be documented, together with some
\emph{evidence} for that behavior.  Most existing BDD tools use
\emph{code examples} as evidence for behavior.
Hspec, a BDD tool for Haskell inspired by RSpec~\cite{rspec}, supports
both code examples and \emph{properties} as evidence.
It can verify examples and test properties, and it can create an
informal specification document from that.

@@

Both, Doctest and Hspec are missing some features.  So we extend them
as needed.  In particular, our contributions are:

@@

\item
    Introduce a set of combinators to set expectations about
    code examples for use with Hspec (Section \ref{sec:code-doc} and Section \ref{sec:hspec-comb})

@@

\item
    Show best current practice of BDD in Haskell, using Doctest and
    Hspec (Section \ref{ref:Best-current-practice})

@@

@@

\item[spec]
    TBD: BDD terminology for test suite.
\end{description}

\begin{quote}
    \emph{sol: Can we remove what follows??}
\end{quote}

\begin{description}
\item[developer]
    A programmer who develops a library.

@@
